Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-17 paper/intro.tex
more wordsmithing

The two automatic transforms discussed in this paper are (1) the insertion of a filter to prevent malformed data from a malicious actor from being propagated to downstream components, and (2) the insertion of a monitor to detect (and alert) unexpected behaviors arising from untrusted components. These transformations not only change the architecture of the model by adding in new components; they also generate a formal specification for the behavior of the inserted high-assurance components in the AGREE language. Those specifications are sufficient for model checking to prove that with the incorporation of these high-assurance components, the hardened system meets its cyber-resiliency requirements.

>>>>

The following security-enhancing transformations are discussed in the
remainder of the paper: (1) the insertion of a filter to prevent
malformed data from a malicious actor from being propagated to
downstream components, and (2) the insertion of a monitor to detect
(and alert) unexpected behaviors arising from untrusted
components. These transformations not only change the architecture of
the model by adding in new components; they also generate a formal
specification for the behavior of the inserted high-assurance
components in the AGREE language. Those specifications are sufficient
for model checking to prove that---due to the incorporation of these
high-assurance components---the hardened system meets its
cyber-resiliency requirements.
